Manuscript 1 code

### 2024-09-13 manuscript_1_code.Rmd
figuring evenness out man

diversity_stability <- alpha_diversity_quad_macro_with_cover %>%
  dplyr::group_by(location, habitat, site) %>%
  dplyr::summarise(
            richness_mean = mean(richness), 
            shannon_mean = mean(shannon), 
            cover_mean = mean(macroalgal_prop_cover),
            cover_cv = CV(macroalgal_prop_cover),
            cover_stability = 1/CV(macroalgal_prop_cover))

diversity_stability_synchrony <- left_join(diversity_stability, lm_synchrony, by = join_by(location))
diversity_stability_synchrony$synchrony_trans <- sv_trans(diversity_stability_synchrony$synchrony)
diversity_stability_synchrony <- na.omit(diversity_stability_synchrony) # remove quads that never had algae --> NaN calcs

dss_ranges<- diversity_stability_synchrony %>%
  group_by(habitat) %>%
  summarise(min_richness = min(richness_mean),
            max_richness = max(richness_mean),
            min_stability= min(cover_stability),
            max_stability = max(cover_stability),
            min_synchrony = min(synchrony_trans),
            max_synchrony = max(synchrony_trans))
```

>>>>

diversity_stability <- alpha_diversity_quad_macro_with_cover %>%
  dplyr::group_by(location, habitat, site) %>%
  dplyr::summarise(
            richness_mean = mean(richness), 
            shannon_mean = mean(shannon), 
            cover_mean = mean(macroalgal_prop_cover),
            evenness_mean = mean(evenness, na.rm = T),
            cover_cv = CV(macroalgal_prop_cover),
            cover_stability = 1/CV(macroalgal_prop_cover))

diversity_stability_synchrony <- left_join(diversity_stability, lm_synchrony, by = join_by(location))
diversity_stability_synchrony$synchrony_trans <- sv_trans(diversity_stability_synchrony$synchrony)
# diversity_stability_synchrony <- na.omit(diversity_stability_synchrony) # remove quads that never had algae --> NaN calcs

dss_ranges<- diversity_stability_synchrony %>%
  group_by(habitat) %>%
  summarise(min_richness = min(richness_mean),
            max_richness = max(richness_mean),
            min_evenness = min(richness_mean, na.rm = TRUE),
            max_evenness = max(richness_mean, na.rm = TRUE),
            min_stability= min(cover_stability, na.rm = TRUE),
            max_stability = max(cover_stability, na.rm = TRUE),
            min_synchrony = min(synchrony_trans, na.rm = TRUE),
            max_synchrony = max(synchrony_trans, na.rm = TRUE))
```
